---
title: "Histogram App (Peer Assignment Part I)"
author: "Leonardo Alvarado"
date: "15/06/2015"
output: pdf_document
---

This documentation explain how to use the application created in **Shiny** which is part of the peer assignment  for the course **Developing Data Products**.

## The Shiny Apllication

The application shows two different histograms:
1. Number of seismic events per year.  
2. Number of seismic events per magnitud.

that ocurred between years 2000 and 2010 in the region of Venezuela (between latitude 5ºN to 14ºN and longitude 58ºW to 74ºW). The database was provided by FUNVISIS (Fundación Venezolana de Investigaciones Sismológicas).

### Controls of the app.
The app contain the following controls:  
- With the **Slider control** you can modify the time period between 2000 and whatever year between 2000 and 2010. (The initial year can't be changed).  
- With the **Numeric Input control** you can modify the region that you want to check. The region should between the coordinates indicates above (Always between 5 to 14 and -74 to -54). A map of the region is in the main panel as a reference, it can't be modified.   
- With the **Select Input control** you can choose between two histogram: Number events per year or Number events per Magnitud.

### Results of the app
1. The histogram showed when you select **Number of events per year** is the following:

```{r, echo=FALSE, fig.height=3}
library(ggplot2)		  
load("datos.RData")
	gg <- ggplot(datos, aes(x=YYYY)) + geom_histogram(binwidth=1,colour="black",fill="blue") +
	  	ylab("No sismos") + theme(axis.text.x = element_text(angle = 0, hjust = 1,size=14,colour="black"),
        axis.title=element_text(size=20,face="bold"), axis.text.y = element_text(hjust = 1,size=14,colour="black"))  
   print(gg)
```



2. The histogram showed when you select **Number of events per Magnitude** is the folowing:

```{r,echo=FALSE,fig.height=4}
library(ggplot2)		  
load("datos.RData")
	gg <- ggplot(datos, aes(x=mag)) + geom_histogram(binwidth=1,colour="black",fill="blue") +
	  	ylab("No sismos") + theme(axis.text.x = element_text(angle = 0, hjust = 1,size=14,colour="black"),
        axis.title=element_text(size=20,face="bold"), axis.text.y = element_text(hjust = 1,size=14,colour="black"))  
   print(gg)
```




