---
title: "Eartquake Histograms "
author: "Leonardo Alvarado"
date: "10/07/2015"
output: html_document
---


This application was designed to plot two type of histograms from real database of earthquakes that occured between 2000 and 2010 in Venezuela.

## The Shiny Aplication

The histograms that can be plotted are: 

1. Number of seismic events per year 

2. Number of seismic events per magnitud,

since 2000 up to selected year (max 2010); you can see the number of eartquake occurred in the region of Venezuela, between latitude 5 to 14ºN and longitude 58 to 74ºW (or -74 to -58), the region of interest can be modified. The database was provided by FUNVISIS (Fundación Venezolana de Investigaciones Sismológicas).

## Controls of the app.
The app contain the following controls:  

- **Slider Control:** To modify the period of time to plot, from 2000 to whatever year between 2000 and 2010. (The initial year can't be changed).  

- **Numeric Input control:** There are 4 controls (latitude min, latitude max, longitude min and longitude max) you can select seismic events in the desired region. The desired region should be between latitude 5 to 14 (ºN) and longitude -74 to -54 (ºW)

- **Select Input control:**  You can choose between two options: **Year** to see the number of events per year or **Magnitude** to see the number events per Magnitud.  

- A **map** of the initial region is located in the main panel as a reference, it can't be modified.   

## Results of the app
1. The histogram plotted when you select Histogram **Year** is the following:

```{r, echo=FALSE, fig.height=3}
library(ggplot2)		  
load("datos.RData")
	gg <- ggplot(datos, aes(x=Year)) + geom_histogram(binwidth=1,colour="black",fill="blue") +
	  	ylab("Count") + theme(axis.text.x = element_text(angle = 0, hjust = 1,size=12,colour="black"),
        axis.title=element_text(size=12,face="bold"), axis.text.y = element_text(hjust = 1,size=12,colour="black"))  
   print(gg)
```

This the histograms of the seismic events per year ocurred in Venezuela between 2000 and 2010.

2. The histogram showed when you select Histogram **Magnitude** is the folowing:

```{r,echo=FALSE,fig.height=3}
library(ggplot2)		  
load("datos.RData")
	gg <- ggplot(datos, aes(x=Magnitude)) + geom_histogram(binwidth=1,colour="black",fill="blue") +
	  	ylab("Count") + theme(axis.text.x = element_text(angle = 0, hjust = 1,size=12,colour="black"),
        axis.title=element_text(size=12,face="bold"), axis.text.y = element_text(hjust = 1,size=12,colour="black"))  
   print(gg)
```

This the histograms of the seismic events per magnitude ocurred in Venezuela between 2000 and 2010




